---
title: "Great American Beer Festival"
date: '2020-10-19'
output: html_document
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

pacman::p_load(tidytuesdayR, tidyverse, scales)

theme_set(theme_light())
```


```{r Load}

tt <- tt_load("2020-10-20")

beer_awards <- tt$beer_awards %>% 
  mutate(medal = factor(medal, levels = c("Gold", "Silver", "Bronze")))

```

```{r Skim}
beer_awards %>% 
  skimr::skim()
```

# Analysis Plan

Each observation is a medal awarded to a beer within a given year. There does not appear to be a unique key, meaning that beers can occur more than once. Some questions to get this analysis started:

> How many medals of each type are awarded? 
> Is this related to the number of award categories?
> Are there states or cities more heavily represented? (Number of brewerys, number of medals)
> Can states be grouped by category of beer?

# EDA

## Mechanics of the contest

```{r}
beer_awards %>% 
  count(medal) %>%
  mutate(n = comma(n,accuracy = 1)) %>% 
  kableExtra::kable(caption = "Number of Medals Awarded")

beer_awards %>% 
  count(category, sort = T) %>% 
  slice_max(order_by = n, n = 20) %>% 
  mutate(category = fct_reorder(category, n)) %>% 
  ggplot(aes(n, category, fill = category)) +
  geom_col(show.legend = F) +
  labs(title = "Top 20 Most Common Categories")
```


```{r}
beer_awards %>% 
  group_by(state) %>% 
  summarise(n_gold = sum(medal == "Gold"),
            n_medal = n()) %>% 
  ggplot(aes(n_medal, n_gold, label = state)) +
  geom_text(check_overlap = T) +
  geom_smooth(method = "lm")+
  scale_y_log10() +
  scale_x_log10() +
  labs(title = "California and Colorado lead the way in medals, Gold or otherwise")
```


